\documentclass[11pt]{article}
\usepackage{graphicx}
\setlength{\parindent}{0pt}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[left=1.06cm,top=1.7cm,right=1.06cm,bottom=0.49cm]{geometry}
\usepackage{xcolor}

% Command for section titles
\newcommand{\sectiontitle}[1]{%
	\vspace{30pt}
	{\large \textbf{#1}} \\
	\rule{\linewidth}{0.4pt}
}

\begin{document}
	
	% ============= HEADER =============
	\begin{center}
		{\LARGE \textbf{CHRISTOPHER GUERRA HERRERO}} \\[6pt]
		+34 603 40 03 27 \quad$\vert$\quad chriss.8.g@gmail.com \quad$\vert$\quad github.com/chriss8g \\[6pt]
	\end{center}
	
	% ============= PROFESSIONAL SUMMARY =============
	\sectiontitle{Professional Summary}
	\vspace{10pt}
	
	Computer Science professional with experience in software development, teaching, and academic research. Noted for leading teams in innovative projects and strong background in mathematics, programming, and modern technologies.
	
	% ============= EDUCATION =============
	\sectiontitle{Education}
	\vspace{10pt}
	
	\textbf{University of Havana} \hfill Havana, Cuba \\
	Bachelor's in Computer Science, GPA: 4.66/5.00 \hfill Apr 2022 – Jun 2025
	
	\vspace{10pt}
	\textbf{Félix Varela Vocational Pre-University Institute of Exact Sciences} \hfill Villa Clara, Cuba \\
	High School Diploma in Exact Sciences, GPA: 99.21/100.00 \hfill Sep 2017 – May 2020
	
	% ============= TECHNICAL SKILLS =============
	\sectiontitle{Technical Skills}
	\vspace{10pt}
	
	\textbf{Languages:} Python, JavaScript, C\#, Java, C/C++, MIPS, PHP \\
	\textbf{Frameworks and APIs:} ReactJS, NextJS, NestJS, ExpressJS, SpringBoot, Angular, Django \\
	\textbf{Tools:} Git, LaTeX, Bash, Strapi, Drupal, WordPress, Scrum, GraphQL \\
	\textbf{Additional Software:} GIMP, Inkscape, Audacity, Unity, Blender, MySQL
	
	% ============= INDUSTRY EXPERIENCE =============
	\sectiontitle{Industry Experience}
	\vspace{10pt}
	
	\textbf{Thor Provider} \hfill Florida, USA \\
	\textbf{Frontend Developer} \hfill Apr 2025 – Present
	\begin{itemize}[left=10pt,itemsep=3pt]
		\item Maintenance of the company’s main website.
		\item Development of a frontend component library.
	\end{itemize}
	
	\vspace{10pt}
	\textbf{Criollos.Tech} \hfill Florida, USA \\
	\textbf{FullStack Developer} \hfill Jun 2024 – Feb 2025
	\begin{itemize}[left=10pt,itemsep=3pt]
		\item Developed the \textit{Cuba Diving} website.
		\item Developed the \textit{Free Skies Championships} website.
		\item Developed the \textit{Reservao} booking management website.
	\end{itemize}
	
	\vspace{10pt}
	\textbf{CITMATEL} \hfill Havana, Cuba \\
	\textbf{FullStack Developer} \hfill Sep 2023 – May 2024
	\begin{itemize}[left=10pt,itemsep=3pt]
		\item Developed a web platform for digitizing records for the Ministry of Technology and Environment.
	\end{itemize}
	
	\vspace{10pt}
	\textbf{AICROS} \hfill Havana, Cuba \\
	\textbf{FullStack Developer (Internship)} \hfill Oct 2023 – Dec 2023
	\begin{itemize}[left=10pt,itemsep=3pt]
		\item Developed a web platform for inventory management for the Ministry of Construction.
	\end{itemize}
	
	\vspace{10pt}
	\textbf{KCN} \hfill Havana, Cuba \\
	\textbf{Development Lead} \hfill Aug 2023 – Present
	\begin{itemize}[left=10pt,itemsep=3pt]
		\item Developed the \textit{LoadUp} delivery platform.
		\item Developed the \textit{Charanga Web} online store.
		\item Developed the \textit{Cubapp} remittance system.
	\end{itemize}
	
	% ============= ACADEMIC EXPERIENCE =============
	\sectiontitle{Academic Experience}
	\vspace{10pt}
	
	\textbf{University of Havana} \hfill Havana, Cuba \\
	\textbf{Instructor} \hfill Feb 2023 – Present
	\begin{itemize}[left=10pt,itemsep=3pt]
		\item Taught Algebra, Numerical Mathematics, and Operating Systems.
		\item Currently teaching Computer Networks and Distributed Systems.
	\end{itemize}
	
	\vspace{6pt}
	\textbf{Numerical Analysis and Image Processing Group (UH)} \hfill Havana, Cuba \\
	\textbf{Researcher} \hfill Jan 2024 – Present
	\begin{itemize}[left=10pt,itemsep=3pt]
		\item Research on integrating neural networks and wavelets in project PN223LH010-036.
	\end{itemize}
	
\end{document}
